\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{titlesec}

\usepackage{tabularx}
\usepackage{calc}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\geometry{left=0.6in, right=0.6in, top=0.6in, bottom=0.6in}

\pagestyle{empty}
\setlength{\parindent}{0pt}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

\titleformat{\subsection}{\bfseries}{}{0em}{}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}

\setlist[itemize]{noitemsep, topsep=4pt, leftmargin=*}
\setlength{\parskip}{1.5pt}

\setstretch{1.0}

\begin{document}

\setlength{\tabcolsep}{0pt}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    {\Huge\bfseries Badiea Al Shabili} &
    \begin{tabular}[c]{r @{\hskip 6pt} l}
        \faIcon{map-marker-alt} & Cyberjaya, Selangor \\
        \faIcon{envelope} & \href{mailto:badiaalshabili@gmail.com}{badiaalshabili@gmail.com} \\
        \faIcon{globe} & \href{https://alshabili.site/}{alshabili.site} \\
        \faIcon{linkedin} & \href{https://www.linkedin.com/in/badia-alshabili}{linkedin.com/in/badia-alshabili} \\
        \faIcon{github} & \href{https://github.com/AlShabiliBadia}{github.com/AlShabiliBadia} \\
        \faIcon{phone} & +60 11 6932 8361
    \end{tabular}
\end{tabular*}
\vspace{6pt}

\section*{Summary}
QA automation engineer passionate about building efficient, scalable, and maintainable testing systems. Skilled in Python, Pytest, and Playwright, with hands-on experience optimizing UI and API test frameworks and integrating CI/CD pipelines. I enjoy improving reliability and developer productivity through automation, data-driven testing, and clean design. Strong foundation in backend development and modern QA practices, with a track record of enhancing test coverage and execution speed.

\section*{Experience}

\subsection*{QA Automation Intern \hfill July 2025 – Present}
\textit{12u12 Sdn Bhd - Cyberjaya, Selangor}
\begin{itemize}[itemsep=2pt]
    \item Built and maintained nearly 1,000 automated UI tests and debugged 400+ legacy scripts, improving stability by 95\% while mentoring a new intern to accelerate onboarding.
    \item Re-architected the test suite from plain Python to a Pytest-based, parameterized framework, reducing duplication by 50\% and enabling large-scale scenario coverage.
    \item Optimized test execution from 3–4 minutes to 4–6 seconds per case through caching and modular data design.
    \item Developed a Gemini-powered AI data extraction tool to automate nutritional data collection and schema validation.
\end{itemize}

\vspace{4pt}

\subsection*{Web Development Intern \hfill March 2022 – June 2022}
\textit{ICT Center - Kajang, Selangor}
\begin{itemize}[itemsep=2pt]
    \item Developed a full-stack IP management web application from scratch using the Laravel framework.
    \item Engineered the backend, implementing all CRUD functionalities and managing the database schema for IP records.
    \item Built the dynamic user interface, creating pages for users to submit, view, and search IP asset data.
\end{itemize}

\section*{Education}

\subsection*{Bachelor of Computer Science (Hons.) \hfill 2023 - 2025}
\textit{Multimedia University - Cyberjaya, Selangor \hfill CGPA: 3.2/4.0}

\vspace{4pt}

\subsection*{Diploma in Software Engineering \hfill 2020 – 2022}
\textit{Infrastructure University Kuala Lumpur - Kajang, Selangor}

\section*{Technical Skills}

\renewcommand{\arraystretch}{1.2} 
\noindent
\begin{tabularx}{\linewidth}{@{} l >{\raggedright\arraybackslash}X @{}}
    \textbf{Languages} & Python, SQL(MySQL, SQLite, PostgreSQL)\\
    \textbf{Test Automation Frameworks} & Playwright, Selenium, Appium, Pytest, Locust\\
    \textbf{QA Methodologies} & Test Design, API Testing, Regression/Integration/UAT\\
    \textbf{Backend \& Core} & FastAPI, REST APIs, Data Structures, Algorithms, OOP \\
    \textbf{Developer Tools \& CI/CD} & Docker, Git, GitHub, Postman, GitHub Actions\\
    \textbf{Familiar With} & JavaScript, Java, PHP, Kotlin, Django, Laravel \\
\end{tabularx}

\section*{Certifications}
\begin{itemize}[itemsep=2pt]
    \item MIT 6.00.1x: Introduction to Computer Science and Programming Using Python
    \item MIT 6.00.2x: Introduction to Computational Thinking and Data Science
    \item CCNAv7: Introduction to Networks
\end{itemize}

\end{document}